---
title: "Build Summary"
output: html_notebook
---

Goal: Create a summary containing all useful data points we would like to analyze

TODO - drop people who hit the same thing all the time

## Load Primary Data

```{r}
library(tidyverse)
source("summary.r")
```

Load the primary data and the metadata

```{r}
data = read.csv("microstudy-data.csv", stringsAsFactors = FALSE) %>%
  mutate(Condition = as.factor(Condition))
meta = read.csv("microstudy-meta.csv", stringsAsFactors = FALSE)
nrow(data)
nrow(meta)
```

Some applicants seem to have held down the keys, resulting in thousands of presses. Remove presses more often than once per second

```{r}
data_clean = dropDuplicateTimes(data)
data_clean
```

## Add response summaries

We add S, I, SI, IS, or X, depending on the response pattern for a given micro condition. 

* S if they hit x one or more times during the condition
* SI if they hit x 1+ times, then z 1+ times
* X if they switched back and forth

```{r}
responses = conditionResponses(data_clean) %>% arrange(Condition, RESP_ID)
```


Add Sensitive and Insenstive Scores

```{r}
fields = list(responses$GayMicro1SI, responses$GayMicro2SI, responses$GayMicro3SI, responses$MuslimMicro1SI, responses$MuslimMicro2SI, responses$MuslimMicro3SI)

scored = responses %>%
  mutate(
    Insensitive = tally(fields, insensitiveScore),
    Sensitive = tally(fields, sensitiveScore)
  ) %>%
  select(RESP_ID, Condition, Insensitive, Sensitive, everything())

scored
```

## Calculate subscales

Cross doesn't use any reverse coded items. It appears CultConceal doesn't either. 

WARNING: watch out for existing summary columns (CultConceal) when using starts_with

```{r}
subscales = meta %>%
  transmute(
    RESP_ID = RESP_ID,
    # I don't have enough information to compute most other scores, because some are reverse coded
    CultConceal = subscale(.,CultConceal1,CultConceal2, CultConceal3, CultConceal4),
    Cross = subscale(., starts_with("Cross"))
  )
subscales
```



## Combine all results 

```{r}
summary = inner_join(scored, subscales, by = "RESP_ID") %>%
  select(RESP_ID, Condition, CultConceal, Cross, Insensitive, Sensitive, everything())
summary
```

```{r}
write.csv(summary, "summary.csv")
```




Look for bad data. No, it looks like simply cleaning it to once/second does enough. They DO change their answers. Just don't count the total number of presses.

```{r}
sample = data %>%
  filter(RESP_ID == "ES20GRE")
sample
```

